### 2019-11-07 report/paper.tex

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& A0207441N & e0445541@u.nus.edu & HOG/HOV \& SVM, Report \\
    David Drews& Axx &e0454245@u.nus.edu & Haar Cascade, Report \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & Histogram Correlation, Report \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}

>>>>

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& A0207441N & e0445541@u.nus.edu & HOG/HOV \& SVM, Report \\
    David Drews & A0209794N & e0454245@u.nus.edu & Haar Cascade, Report \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & Histogram Correlation, Report \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}
